Data Management \\ and LSST Special Programs

### 2022-02-24 DMTN-065.tex
updates post-GPDF disc

\subsubsection{Data Products}

@@

\subsubsection{Metadata}

@@

\subsubsection{Processing}

It is a requirement that Special Programs processing with the Prompt pipeline (or a reconfigured version of it) is subject to the same timescales and latency constraints of 24 hours for the release of Prompt data products and 1 minute for the transmission of Alert packets (DMS-REQ-0344).

@@

\subsubsection{User Processing}

@@

It would be both possible and scientifically beneficial to include all standard and alternative standard visits from Special Programs in Prompt processing and Alert Production, alongside the standard visits from the WFD Main Survey.

@@

\subsection{Anticipated Rubin Science Platform Capabilities for Special Programs }

@@

>>>>

\subsubsection{Data Products}\label{sssec:proc_reqs_dp}

@@

\subsubsection{Metadata}\label{sssec:proc_reqs_meta}

@@

\subsubsection{Processing}\label{sssec:proc_reqs_proc}

It is a requirement that any Special Programs processing done with the Prompt pipeline (or a reconfigured version of it) is subject to the same timescales and latency constraints of 24 hours for the release of Prompt data products and 1 minute for the transmission of Alert packets (DMS-REQ-0344).

@@

\subsubsection{User Processing}\label{sssec:proc_reqs_ug}

@@

It is expected that all Special Programs data that {\it can} be processed by the Prompt processing and Alert Production pipelines {\it would} be, alongside the standard visits from the WFD Main Survey, as this would be scientifically beneficial to the science pillars of the LSST.

@@

\subsection{``Discoverability Considerations" (Visit Labels)}

\begin{itemize}
\item needs for labelling
\item survey characterizability, selection biases
\item provenance and origin
\item not just for separate data products but all regions
\item what if someone puts a micro survey in NES? labeling useful
\end{itemize}

\subsection{Anticipated Rubin Science Platform Capabilities for Special Programs}

@@

\subsection{Computational Resources for User (Re-)Processing}

As mentioned in Section~\ref{sssec:proc_reqs_ug}, Rubin Observatory will reserve 10\% of its total data processing capacity for users.
This component would include {\it all} user processing and re-processing of any and all LSST data, including Special Programs.

As described in Section~\ref{ssec:proc_spdp} this processing capacity will be accessed via Rubin Science Platform, with a supported software environment and infrastructure for batch processing \citedsp{dmtn-202}.

Very computationally intense processing (e.g., shift-and-stack for faint moving objects) will likely require external resources\footnote{For more details about the boundary between what Rubin Observatory will provide (in terms of data products and processing resources) and what will be left to the expertise of the science community, see \url{https://www.lsst.org/about/dm/data-products}}.
